---
title: "morning activity"
format: html
editor: visual
execute: 
  echo: false
  message: false
---

```{r}
library(lterdatasampler)
library(tidyverse)
library(kableExtra)
```

The graph below shows the relationship between fiddler crab size in millimeters and latitude throughout the eastern coast of the United States. In general, crab sizes increase toward higher latitude.

```{r}
fiddler_plot <- ggplot(data = pie_crab, aes(x = size, y = latitude)) +
  geom_jitter(aes(color = latitude)) 
  #|fig_cap: this is my caption

fiddler_plot
```

The table below shows the mean size, standard deviation, and count of fiddler crabs at each Site.

```{r}
summary <- pie_crab |>
  group_by(site) |>
  summarize(mean_size = round(mean(size), 2), 
            sd_size = round(sd(size), 2),
            count = n()) |> 
  kable(col.names = c("Site", "Mean Size (mm)", "Size Standard Deviation (mm)", "Count")) |> 
  kable_styling(bootstrap_options = "striped")
  
summary
            
```

Citation:

-   Johnson, D. 2019. Fiddler crab body size in salt marshes from Florida to Massachusetts, USA at PIE and VCR LTER and NOAA NERR sites during summer 2016. ver 1. Environmental Data Initiative. <https://doi.org/10.6073/pasta/4c27d2e778d3325d3830a5142e3839bb> (Accessed 2021-05-27).

-   Johnson DS, Crowley C, Longmire K, Nelson J, Williams B, Wittyngham S. The fiddler crab, Minuca pugnax, follows Bergmann\'s rule. Ecol Evol. 2019;00:1--9. <https://doi.org/10.1002/ece3.5883>

\
